\paperTitle

### 2014-01-31 doc/icml2014/undirected.tex

% DONE: need more of a transition from previous sections
Recall that we used tensor factorization and composite likelihood
to estimate the latent marginals $Z_\sC = \BP(\vh_\sC)$ and $\mOpp{v}{i} = \BP(x_v \mid h_i)$.
For directed models, obtaining the local conditional tables from $Z_\sC$ requires
renormalizing $Z_\sC$.
For undirected log-linear models, the parameters cannot simply be obtained locally;
we will have to perform global optimization.
Fortunately, as we will show, this optimization problem is convex,
by relating the recovered conditional moments with the sufficient statistics of
the log-linear model.

>>>>

% DONE: need more of a transition from previous sections
Recall that we used tensor factorization and composite likelihood
to estimate the hidden marginals $Z_\sC = \BP(\vh_\sC)$ and $\mOpp{v}{i} = \BP(x_v \mid h_i)$.
For directed models, obtaining the local conditional tables from $Z_\sC$ requires
renormalizing $Z_\sC$.
For undirected log-linear models, the parameters cannot simply be obtained locally;
we will have to perform global optimization.
Fortunately, as we will show, this optimization problem is convex,
by relating the recovered conditional moments with the sufficient statistics of
the log-linear model.
